Manuscript_Tables_LongCovid

### 2023-05-31 characterisation/Manuscript_Tables_Figures.Rmd
first version

get_rr_first_reinfection_plot <- function(data){
plot <- RR_data  %>%
    ggplot(aes(
      x = relative_risk,
      y = reorder(symptom, -relative_risk),
      xmin = low_ci,
      xmax = up_ci,
      shape = database,
      color = database)) +
    geom_point(size = 2, position = position_dodge(width = 1)) +
    geom_errorbar(width = 0, size = 1, position = position_dodge(width = 1)) +
    scale_y_discrete(expand=c(0,0), position = "left") +
     scale_x_log10(breaks = c(0.1, 0.2, 0.4, 0.6, 0.8, 1),
                   labels = c("0.1", "0.2", "0.4","0.6", "0.8", "1"),
                  limits = c(0.04, 1.2)
                  ) +  
    scale_colour_manual(values = c(col1, col2)) +
    geom_vline(
      xintercept = 1, colour = "#000000",
      linetype = 1
    ) +
    mytheme +
    xlab("\nRR (with 95% CI)") +
    ylab("")  +
    guides(color = guide_legend(title = "Database"),
           shape = guide_legend(title = "Database")) +
    geom_hline(yintercept = c(1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5,10.5,11.5,
                     12.5,13.5,14.5,15.5,16.5,17.5,18.5,19.5,20.5,21.5,22.5,23.5),
                linetype = "dashed",
               color = "#D2D6DB"
    )
plot
}

@@

### Relative Risks - infections vs all negative tests
#### 1. Table: RR of long COVID symptoms, COVID-19 infection vs all SARS-CoV-2 negative tests - 90 days
```{r}
table_RR_90 <- get_RR(sidiap_data = RR_new_covid_tested_negative_earliest_90days_SIDIAP,
                  cprd_data = RR_new_covid_tested_negative_earliest_90days_CPRD)
table_RR_90
```

@@

#### 3. Table: RR of long COVID symptoms, COVID-19 infection vs all SARS-CoV-2 negative tests - 28 days
```{r}
table_RR_28 <- get_RR(sidiap_data = RR_new_covid_tested_negative_earliest_28days_SIDIAP,
                  cprd_data = RR_new_covid_tested_negative_earliest_28days_CPRD)
table_RR_28
```

>>>>

get_rr_first_reinfection_plot <- function(data){
plot <- RR_data  %>%
    ggplot(aes(
      x = relative_risk,
      y = reorder(symptom, -relative_risk),
      xmin = low_ci,
      xmax = up_ci,
      shape = database,
      color = database)) +
    geom_point(size = 2, position = position_dodge(width = 1)) +
    geom_errorbar(width = 0, size = 1, position = position_dodge(width = 1)) +
    scale_y_discrete(expand=c(0,0), position = "left") +
     scale_x_log10(breaks = c(0.1, 0.2, 0.4, 0.6, 0.8, 1),
                   labels = c("0.1", "0.2", "0.4","0.6", "0.8", "1"),
                  limits = c(0.035, 1.2)
                  ) +  
    scale_colour_manual(values = c(col1, col2)) +
    geom_vline(
      xintercept = 1, colour = "#000000",
      linetype = 1
    ) +
    mytheme +
    xlab("\nRR (with 95% CI)") +
    ylab("")  +
    guides(color = guide_legend(title = "Database"),
           shape = guide_legend(title = "Database")) +
    geom_hline(yintercept = c(1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5,10.5,11.5,
                     12.5,13.5,14.5,15.5,16.5,17.5,18.5,19.5,20.5,21.5,22.5,23.5),
                linetype = "dashed",
               color = "#D2D6DB"
    )
plot
}

@@

### Relative Risks - infections vs all negative tests
#### 1. Table: RR of long COVID symptoms, COVID-19 infection vs all SARS-CoV-2 negative tests - 90 days
```{r}
table_RR_90 <- get_RR(sidiap_data = RR_new_covid_tested_negative_all_90days_SIDIAP,
                  cprd_data = RR_new_covid_tested_negative_all_90days_CPRD)
table_RR_90
```

@@

#### 3. Table: RR of long COVID symptoms, COVID-19 infection vs all SARS-CoV-2 negative tests - 28 days
```{r}
table_RR_28 <- get_RR(sidiap_data = RR_new_covid_tested_negative_all_28days_SIDIAP,
                  cprd_data = RR_new_covid_tested_negative_all_28days_CPRD)
table_RR_28
```
